\section{Semantic tracker}

\subsection{Semantic knowledge update}
With some successfully tracked objects, we may adaptively update the semantic scene. 
More specifically, we update the corresponding topics with well-tracked objects, which are those enter through the entry area, tightly follow its belonging topic, and successfully exit through exit areas. 
The scene is updated as follows: 
The first and last location, along with the direction of a high-quality trajectory is used to update the entry/exit candidates; the rectangle perpendicular width wrt. its topic is used to update the topic perpendicular within its extent, where the updated value remains the mean of all the updates.
By such iterative updating, we have more representative scene knowledge regarded to object tracking. The entry/exit area may gradually shift to where most objects actually enter and exit, where the perpendicular width of each topic also better fits the object statistics. The entire process is described in Algorithm \ref{alg:semantic-tracker} to \ref{alg:semantic-tracker-entry}.

\begin{algorithm}
 \caption{Tracking with semantic knowledge.}
 \label{alg:semantic-tracker}
 % \KwData{$K$ visual topics, corresponding entry/exit area and direction.}
 \begin{algorithmic}[1]
 \For{each frame $t$} 
     \State Topic model inference on the frame.
     \State Obtain foreground boxes $\mathbf{R}_{bg} = \{\bm{r}_{bg}\}$.
     \State Obtain detection boxes $\mathbf{R}_{det} = \{\bm{r}_{det}\}$.
     \For{each $i$ th object $O_i$ at $\bm{r}_{t-1}(i), \quad(i = 1, \dots, N_t)}$
        \State Get topic assignment $k_t(i)$.
        \State Find the most matched boxes $\bm{r}_{bg}(i)$ and $\bm{r}_{det}(i)$ with $\bm{r}_{t-1}(i)$.
        \State $\mathbf{R}_{bg} = \mathbf{R}_{bg}\setminus\bm{r}_{bg}(i), \mathbf{R}_{det} = \mathbf{R}_{det}\setminus\bm{r}_{det}(i).$
        \State Compute mean velocity $\bm{v}(i)$ within $\bm{r}_{t-1}(i)$ from the optical flow.
        \State Make measurement for tracking update $\bm{z}_t(i) = [\bm{r}_{bg}(i), \bm{r}_{det}(i), \bm{v}(i)]$.
        \State Set measurement covariance error $R$.
        \State Update object tracker with $\bm{z}_t(i)$ and $R$, get result $\bm{r}_{t}(i)$.
        \State CheckExitSemantic$(O_i, \bm{r}_t(i), k_t(i), t)$
     \EndFor
     \For{Each remaining box candidate $r\in\{\mathbf{R}_{bg}\bigcup\mathbf{R}_{det}\}$}
      \State CheckEntrySemantic$(\bm{r})$.
     \EndFor
\EndFor
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
 \caption{CheckExitSemantic$(O, \bm{r}, k, t)$}
 \label{alg:semantic-tracker-exit}
 \begin{algorithmic}[1]
\If{$O$ is in extended tracking phase} 
  \If{$S_{\text{extend}}(\bm{r}, k, t) <=\sigma_{4}$}
    \State Exit object.
%             update semantic scene\;
  \EndIf
\ElsIf{$S_{\text{track}}(\bm{r}, k, t)<\sigma_{3}$} 
  \State Discard object.
\EndIf
\If{$S_\text{exit}(\bm{r}, k) > \sigma_2$} 
  \State Enter extended tracking phase.
\EndIf
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
 \caption{CheckEntrySemantic$(\bm{r})$}
 \label{alg:semantic-tracker-entry}
 \begin{algorithmic}[1]
\State Get the topic $k$ for $\bm{r}$ at this frame.
\If{$S_\text{entry}(\bm{r}, k) > \sigma_{1}$}
  \State Initialize object.
\EndIf
\end{algorithmic}
\end{algorithm}
