\acknowledgment

% A page or two so of shout-outs to people you appreciate.  Don't forget
% your advisor and committee members!
I would like thank my advisor Dr. Jakob Eriksson throughout these years for his support and instructions.
He is very visionary to pick this interesting and challenging project. 
I appreciated the time he spent with me to learn together.
I still remember the time that we went through the code line by line, trying to find a hidden bug; or discussed some algorithm for hours. 
Thanks to the generous freedom, I become independent and mature in research.

Also, I would like express appreciation to my committee members, for their advice and inspiration. Most of them are from classes I have taken, where I learned the fundamental knowledge for my research. Specifically I want to thank Dr. Xinhua Zhang, whose rigorous attitude toward research and passion of teaching greatly inspired me. Dr. Jie Yang gave me helpful guidance of many technical questions.

In addition, I want to thank my parents and sister.
This thesis would not exist without their unconditional love and support. 
My father teaches me to be strong and tough; my mother supports me for all my big decisions; my sister takes care of my parents when I am far away.
I know they will always be there for me, even on the other side of the world.
Finally, special thanks to Sihong Xie, for his accompany and encouragement along this tough journey. 
I am grateful that we participate and witness each other's growth.
% This line is required, but of course replace my initials with yours.
\initials{YJ}